---
title: "R & R"
author: "Jacob Oursland & Elijah Grimshaw"
date: "February 14, 2017"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{r, include=FALSE}
require(jsonlite)
require(parsedate)
require(lubridate)

orig <- jsonlite::fromJSON("r-commits.json", simplifyDataFrame=TRUE)
edit <- orig
df <- orig

for (i in 50455:1) {
  edit[50456-i,2] <- i
}

edit$date <- as_date(edit$date)
df$date <- parse_date(df$date)
auth <- table(edit$author)

```

##Inspiration

[**Video**](gource.mp4)

## Collecting the Data

1. Clone the R source git repository: [**https://github.com/wch/r-source**](https://github.com/wch/r-source)
2. Use a script that parses `git --log` into a JSON file that contains each commit, the author, date, paths modified, and lines changed to each file.
3. Use R on R!

##Commits Over Time
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(edit$commit ~ edit$date, xlab="Year", ylab="Commits")
abline(lm(edit$commit ~ edit$date), col="red")
```

##Size of Commits over Time
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(df$net~df$date, xlab ="Year", ylab="Lines Change")
```

##Overview
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(edit[,-c(1,6,8)])
```

##Commits per Author
```{r, echo=FALSE, warning=FALSE, message=FALSE}
require(lattice)
barchart(auth, xlab="Commits", ylab="Authors", cex.axis=.60, las=2)
```


##Commit Sizes for Author
```{r, echo=FALSE, warning=FALSE, message=FALSE}
with(edit, bwplot(author~log10(abs(net)), xlab="Order of Change"))
```

##Conclusions

1. R is maintained by a core team, of which there are only about 4 major contributors.
2. Most large commits (features?) are by those 4 major contributors.
3. The other contributors are primarily involved in smaller commits (bugfixes?).

##Further Exploration

1. Whose code experiences rapid turnover?
2. For each author, what are the statistics on average cyclomatic complexity index of their code?
3. Are 1 and 2 correlated?
